Short Paper

### 2022-01-21 AppHumanGHY.Rmd
updated Readme; added bibliography

journal: "An awesome journal"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
csl: aag.csl
output: rticles::elsevier_article
---

>>>>

journal: "An awesome journal"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
#linenumbers: true
#numbersections: true
csl: aag.csl
output: rticles::elsevier_article
---
